Figures

### 2019-04-09 code/figures.rmd
Added .gitignore for caching folders
Added tau2 vs. effect size faceted by effect type (NB! OR = SMD)

@@

@@

ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
```

>>>>

#Plots of H2 and I2 vs. fisher's z for all effects together

@@

```{r corr_per_effect_type, cache = TRUE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference",
                              'Raw mean difference' = "Mean Difference",
                              'Risk difference' = "Risk Difference",
                              'r' = "Correlation")) %>% 
  left_join(tau2_per_type) %>% 
  mutate(eff_size = abs(eff_size)) #need the absolute values for plotting

fitter <- function(df){ #function to fit correlations for annotating facet plots
 fit <- summary(lm(tau2 ~ eff_size, data = df))
 data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
}

labels <- tau2_per_type %>% 
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>% 
  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting

tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different

tau2_facet
# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)

@@

#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
```
